Metadata control

### 2022-10-13 metadata/metadata_control.Rmd
Adding MAAs to standards list

```{r grabstans}
if(!file.exists("raw_data/raw_stans.csv")){
  raw_stans <- read.csv(paste0(
    "https://raw.githubusercontent.com/IngallsLabUW/Ingalls_Standards",
    "/master/Ingalls_Lab_Standards.csv"
  ))
  write.csv(raw_stans, file = "raw_data/raw_stans.csv", row.names = FALSE)
}
raw_stans <- read.csv("raw_data/raw_stans.csv")
clean_stans <- raw_stans %>%
  filter(Column=="HILIC") %>%
  mutate(polarity=ifelse(str_detect(z, "-"), "neg", "pos")) %>%
  mutate(mz=as.numeric(mz)) %>%
  mutate(peak_quality=str_extract(Peak_Quality, "Yes|No|Problematic")) %>%
  select(compound_type=Compound_Type, compound_name=Compound_Name,
         compound_name_old=Compound_Name_Original,
         formula=Empirical_Formula, rt=RT_minute, mz=mz, 
         ionization_form=Ionization_Form,
         charge=z, kegg_id=KEGG_Code, polarity, conc_um=Concentration_uM,
         date_added=Date_Added, mix=HILIC_Mix, priority=Priority,
         peak_quality) %>%
  add_row(compound_type="Custom", compound_name="Bisulfate",
          compound_name_old="Bisulfate", formula="HSO4", rt=13, 
          mz=95.95172965+1.007276, ionization_form="[M]", 
          charge=-1, date_added=150101, polarity="neg") %>%
  add_row(compound_type="Custom", compound_name="Bromine81",
          compound_name_old="Bromine upper", formula="Br(81)", rt=7, 
          mz=80.91563, ionization_form="[M]", charge=-1, 
          date_added=150101, polarity="neg") %>%
  add_row(compound_type="Custom", compound_name="Bromine79",
          compound_name_old="Bromine lower", formula="Br(79)", rt=7, 
          mz=78.91768, ionization_form="[M]", charge=-1, 
          date_added=150101, polarity="neg") %>%
  add_row(compound_type="Custom", compound_name="Pyro from glutamine?",
          compound_name_old=compound_name, formula="C5H7NO3", rt=11, 
          mz=130.050419, ionization_form="[M-NH3+H]", charge=-1, 
          date_added=150101, polarity="pos") %>%
  add_row(compound_type="Custom", compound_name="Pyro from glutamate?",
          compound_name_old=compound_name, formula="C5H7NO3", rt=12, 
          mz=130.050419, ionization_form="[M-H2O+H]", charge=-1, 
          date_added=150101, polarity="pos") %>%
  # add_row(compound_type="Custom", compound_name="Deoxyguanosine?",
  #         compound_name_old=compound_name, formula="C10H13N5O4", rt = 4.5,
  #         mz=268.10403, ionization_form="[M+H]", charge=1, 
  #         date_added=150101, polarity="pos") %>%
  add_row(compound_type="Custom", compound_name="Deoxycytidine?",
          compound_name_old=compound_name, formula="C10H13N5O4", rt = 6.6,
          mz=228.09788, ionization_form="[M+H]", charge=1, 
          date_added=150101, polarity="pos") %>%
  add_row(compound_type="Custom", compound_name="Homoserine betaine?",
          compound_name_old=compound_name, formula="C7H15NO3", rt = 6.7,
          mz=162.1125, ionization_form="[M+H]", charge=1, 
          date_added=150101, polarity="pos") %>%
  add_row(compound_type="Custom", compound_name="Threonine betaine?",
          compound_name_old=compound_name, formula="C7H15NO3", rt = 5,
          mz=162.1125, ionization_form="[M+H]", charge=1, 
          date_added=150101, polarity="pos") %>%
  add_row(compound_type="Custom", compound_name="Theanine?",
          compound_name_old=compound_name, formula="C7H14N2O3", rt = 6.8,
          mz=175.10771, ionization_form="[M+H]", charge=1, 
          date_added=150101, polarity="pos") %>%
  mutate(date_added=strptime(x = date_added, format = "%y%m%d"))
write.csv(clean_stans, file = "made_data/clean_stans.csv", row.names = FALSE)
```

>>>>

```{r grabstans}
if(!file.exists("raw_data/raw_stans.csv")){
  raw_stans <- read.csv(paste0(
    "https://raw.githubusercontent.com/IngallsLabUW/Ingalls_Standards",
    "/master/Ingalls_Lab_Standards.csv"
  ))
  write.csv(raw_stans, file = "raw_data/raw_stans.csv", row.names = FALSE)
}
raw_stans <- read.csv("raw_data/raw_stans.csv")
clean_stans <- raw_stans %>%
  filter(Column=="HILIC") %>%
  mutate(polarity=ifelse(str_detect(z, "-"), "neg", "pos")) %>%
  mutate(mz=as.numeric(mz)) %>%
  mutate(peak_quality=str_extract(Peak_Quality, "Yes|No|Problematic")) %>%
  select(compound_type=Compound_Type, compound_name=Compound_Name,
         compound_name_old=Compound_Name_Original,
         formula=Empirical_Formula, rt=RT_minute, mz=mz, 
         ionization_form=Ionization_Form,
         charge=z, kegg_id=KEGG_Code, polarity, conc_um=Concentration_uM,
         date_added=Date_Added, mix=HILIC_Mix, priority=Priority,
         peak_quality) %>%
  add_row(compound_type="Custom", compound_name="Bisulfate",
          compound_name_old="Bisulfate", formula="HSO4", rt=13, 
          mz=95.95172965+1.007276, ionization_form="[M]", 
          charge=-1, date_added=150101, polarity="neg") %>%
  add_row(compound_type="Custom", compound_name="Bromine81",
          compound_name_old="Bromine upper", formula="Br(81)", rt=7, 
          mz=80.91563, ionization_form="[M]", charge=-1, 
          date_added=150101, polarity="neg") %>%
  add_row(compound_type="Custom", compound_name="Bromine79",
          compound_name_old="Bromine lower", formula="Br(79)", rt=7, 
          mz=78.91768, ionization_form="[M]", charge=-1, 
          date_added=150101, polarity="neg") %>%
  add_row(compound_type="Custom", compound_name="Pyro from glutamine?",
          compound_name_old=compound_name, formula="C5H7NO3", rt=11, 
          mz=130.050419, ionization_form="[M-NH3+H]", charge=-1, 
          date_added=150101, polarity="pos") %>%
  add_row(compound_type="Custom", compound_name="Pyro from glutamate?",
          compound_name_old=compound_name, formula="C5H7NO3", rt=12, 
          mz=130.050419, ionization_form="[M-H2O+H]", charge=-1, 
          date_added=150101, polarity="pos") %>%
  # add_row(compound_type="Custom", compound_name="Deoxyguanosine?",
  #         compound_name_old=compound_name, formula="C10H13N5O4", rt = 4.5,
  #         mz=268.10403, ionization_form="[M+H]", charge=1, 
  #         date_added=150101, polarity="pos") %>%
  add_row(compound_type="Custom", compound_name="Deoxycytidine?",
          compound_name_old=compound_name, formula="C10H13N5O4", rt = 6.6,
          mz=228.09788, ionization_form="[M+H]", charge=1, 
          date_added=150101, polarity="pos") %>%
  add_row(compound_type="Custom", compound_name="Homoserine betaine?",
          compound_name_old=compound_name, formula="C7H15NO3", rt = 6.7,
          mz=162.1125, ionization_form="[M+H]", charge=1, 
          date_added=150101, polarity="pos") %>%
  add_row(compound_type="Custom", compound_name="Threonine betaine?",
          compound_name_old=compound_name, formula="C7H15NO3", rt = 5,
          mz=162.1125, ionization_form="[M+H]", charge=1, 
          date_added=150101, polarity="pos") %>%
  add_row(compound_type="Custom", compound_name="Theanine?",
          compound_name_old=compound_name, formula="C7H14N2O3", rt = 6.8,
          mz=175.10771, ionization_form="[M+H]", charge=1, 
          date_added=150101, polarity="pos") %>%
  add_row(compound_type="Custom", compound_name="Asterina-330",
          compound_name_old=compound_name, formula="C12H20N2O6", rt = 10.5,
          mz=289.1393, ionization_form="[M+H]", charge=1) %>%
  add_row(compound_type="Custom", compound_name="Shinorine",
        compound_name_old=compound_name, formula="C13H20N2O8", rt = 11.6,
        mz=333.1292, ionization_form="[M+H]", charge=1) %>%
  add_row(compound_type="Custom", compound_name="Palythine",
        compound_name_old=compound_name, formula="C10H16N2O5", rt = 11.0,
        mz=245.1132, ionization_form="[M+H]", charge=1) %>%
  add_row(compound_type="Custom", compound_name="Porphyra-334?",
        compound_name_old=compound_name, formula="C14H22N2O8", rt = 8.1,
        mz=347.1449, ionization_form="[M+H]", charge=1) %>%
  add_row(compound_type="Custom", compound_name="Mycosporine-2-glycine?",
        compound_name_old=compound_name, formula="C12H18N2O7", rt = 11.3,
        mz=303.1186, ionization_form="[M+H]", charge=1) %>%
  add_row(compound_type="Custom", compound_name="Palythene/Usujirene?",
        compound_name_old=compound_name, formula="C13H20N2O5", rt = 8.3,
        mz=285.1445, ionization_form="[M+H]", charge=1) %>%
  add_row(compound_type="Custom", compound_name="Also Palythene/Usujirene?",
        compound_name_old=compound_name, formula="C13H20N2O5", rt = 6.9,
        mz=285.1445, ionization_form="[M+H]", charge=1) %>%
  add_row(compound_type="Custom", compound_name="Mycosporine-glycine?",
        compound_name_old=compound_name, formula="C10H15NO6", rt = 10,
        mz=246.0972, ionization_form="[M+H]", charge=1) %>%
  add_row(compound_type="Custom", compound_name="Also mycosporine-glycine?",
        compound_name_old=compound_name, formula="C10H15NO6", rt = 9.5,
        mz=246.0972, ionization_form="[M+H]", charge=1) %>%
  mutate(date_added=strptime(x = date_added, format = "%y%m%d"))
write.csv(clean_stans, file = "made_data/clean_stans.csv", row.names = FALSE)
```
